Full-day, in home validation of infant body position measurements from inertial sensors

### 2023-02-18 manuscript.Rmd
paneled age graph

```{r age, warning=FALSE, fig.cap="Age trends", fig.align="center", fig.width=5, fig.height=8}
fullday <- read_csv("data/imu-compiled.csv") %>% 
  mutate(id_uni = factor(id*100+session),
         group = factor(ifelse(age <= 8, "Younger", "Older")),
         nap_time = ifelse(is.na(sit_time), nap_time, NA))
fullday_long <- fullday %>% pivot_longer(cols = sit_time:upright_time, names_to = "position", values_to = "prop") %>% 
  mutate(position = factor(position,
                           levels = c("upright_time", "sit_time", "prone_time", "supine_time", "held_time"),
                           labels = c("Upright", "Sitting", "Prone", "Supine", "Held"))) %>% 
  arrange(position, age)

outlier_ids <- c(10701, 10401, 10601)
fullday %>% cor_mat(age, sit_time:upright_time) %>% cor_mark_significant()
fullday %>% filter(!(id_uni %in% outlier_ids)) %>% cor_mat(age, sit_time:upright_time) %>% cor_mark_significant()

fullday_long %>% drop_na(prop) %>% 
  ggplot() + facet_wrap("position", as.table = T, ncol = 2) + 
  geom_smooth(aes(x = age, y = prop), color = "darkgray", method = "lm", se = T) + 
  stat_summary(fun = "mean", mapping = aes(x = age, y = prop, group = id_uni, fill = position), shape = 21, size = .75) + 
  scale_fill_manual(values = pal, guide = "none") + 
  scale_x_continuous(name = "Age (months)", breaks = seq(3, 15, 3), limits = c(3,15)) + 
  ylim(0,1) + ylab("Proportion of waking day")

fullday_long %>% group_by(position, group) %>% get_summary_stats(prop)

>>>>

```{r age, warning=FALSE, fig.cap="Age trends", fig.align="center", fig.width=7.5, fig.height=7}
fullday_group <- read_csv("data/imu-compiled.csv") %>% 
  mutate(id_uni = factor(id*100+session),
         group = factor(ifelse(age <= 8, "Younger", "Older")),
         nap_time = ifelse(is.na(sit_time), nap_time, NA))
fullday_split <- read_csv("data/imu-compiled-split.csv") %>% 
  mutate(id_uni = factor(id*100+session),
         group = factor(ifelse(age <= 8, "Younger", "Older")),
         nap_time = ifelse(is.na(sit_time), nap_time, NA))
fullday <- list("group" = fullday_group, "split" = fullday_split)

fullday_long <- function(ds) {
  ds %>% pivot_longer(cols = sit_time:upright_time, names_to = "position", values_to = "prop") %>% 
  mutate(position = factor(position,
                           levels = c("upright_time", "sit_time", "prone_time", "supine_time", "held_time"),
                           labels = c("Upright", "Sitting", "Prone", "Supine", "Held"))) %>% 
  arrange(position, age)
}

age_scatter <- function(ds) {
  ds %>% drop_na(prop) %>% 
  ggplot() + facet_wrap("position", as.table = T, ncol = 2) + 
  geom_smooth(aes(x = age, y = prop), color = "#191919", method = "lm", se = T) + 
  stat_summary(fun = "mean", mapping = aes(x = age, y = prop, group = id_uni, fill = position), shape = 21, size = .75, alpha = .7) + 
  scale_fill_manual(values = pal, guide = "none") + 
  scale_x_continuous(name = "Age (months)", breaks = seq(3, 15, 3), limits = c(3,15)) + 
  ylim(0,1) + ylab("Proportion of waking day")
}

age_plots <- map(fullday, fullday_long) %>% map(age_scatter)
age_plots <- map2(age_plots, c("A. Group Models", "B. Individual Models"), ~ .x + ggtitle(.y))
age_plots[[1]] + age_plots[[2]]

# outlier_ids <- c(10701, 10401, 10601)
# fullday %>% cor_mat(age, sit_time:upright_time) %>% cor_mark_significant()
# fullday %>% filter(!(id_uni %in% outlier_ids)) %>% cor_mat(age, sit_time:upright_time) %>% cor_mark_significant()
# 
# fullday_long %>% group_by(position, group) %>% get_summary_stats(prop)
